Collaborative Visual Analysis on the Web with RCloud

### 2015-03-31 relatedwork.tex

\begin{figure*}
\centering
\includegraphics[width=.8\linewidth]{fig/notebook/notebook.pdf}
\caption{\label{fig:notebook}An RCloud notebook is a sequence of
  \emph{cells}, each a snippet of source in R or Markdown. Notebooks
  are stored in GitHub \emph{gists}, which provide the version-control
  primitives needed in RCloud during editing (left) or viewing and
  executing (right).}
\end{figure*}

>>>>

\begin{figure*}
\centering
\includegraphics[width=.95\linewidth]{fig/notebook/notebook.pdf}
\caption{\label{fig:notebook}An RCloud notebook is a sequence of
  \emph{cells}, each a snippet of source in one of the supported languages (typically R, but Python and others are also supported) or Markdown. The main creation workflow involves editing notebooks, which are transparently stored as git repositories in GitHub, which provides us with easy access primitives for version tracking. Notebooks can be executed as they're edited (left), or in a standalone viewer (right), via a slightly different URL. This lightweight provides a very low-friction mechanism for sharing results which we discuss in full in Section~\ref{where}. }
\end{figure*}
